Towards Comparable Active Learning

### 2023-05-18 doc/al_benchmark_paper.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sampling Strategies}\label{sec:sampling_strategies}
\paragraph{Uncertainty Sampling}
\paragraph{BALD}
\paragraph{BADGE}
\paragraph{Coreset}
\paragraph{TypiClust}
%
\subsubsection{Honorable Mentions}
\paragraph{Learning Loss for AL}
Introduces an updated classification model training via an auxiliary loss and therefore cannot be compared fairly against classification models without this boosted training regime.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sampling Strategies}\label{sec:sampling_strategies}
\paragraph{Uncertainty Sampling}
\paragraph{BALD}
\paragraph{BADGE}
\paragraph{Coreset}
\paragraph{TypiClust}
%
\subsubsection{Honorable Mentions}
\paragraph{Learning Loss for AL}
Introduces an updated classification model training with an auxiliary loss and therefore cannot be compared fairly against classification models without this boosted training regime.
